% Abstract: Keep brief and self-contained, one paragraph, 4-6 sentences.
% Should state: (1) problem/motivation, (2) approach, (3) key results, (4) significance.

Full-duplex voice agents—systems that listen and speak simultaneously—are rapidly moving from research to production. However, existing evaluations address conversational dynamics and task completion in isolation. We introduce $\tau$-voice, a benchmark for evaluating voice agents on grounded tasks with real-world complexity: agents must navigate complex multi-turn conversations, adhere to domain policies, and interact with the environment. The framework extends $\tau^2$-bench into a novel voice agent benchmark combining verifiable completion of complex grounded tasks, full-duplex interaction, and realistic audio—enabling direct comparison between voice and text performance. A controllable and realistic voice user simulator provides diverse accents, realistic audio environments, and rich turn-taking dynamics; by decoupling simulation from wall-clock time, the user simulator can use the most capable LLM without real-time constraints. We evaluate task completion (pass@1) and voice interaction quality across 278 tasks: while GPT-5 (reasoning) achieves \textbf{85\%}\revised{Was 80\%; updated text baselines from revised airline/retail tasks.}, voice agents reach only \textbf{31--51\%}\revised{Was 29--42\%; range shifted by new OpenAI model (gpt-realtime-1.5) and Google improvement (29\%$\to$31\% Clean).} under clean conditions and \textbf{25--38\%}\revised{Was 19--30\%; all providers improved, especially OpenAI.} under realistic conditions with noise and diverse accents—a \textbf{47--59pp gap}\revised{Was 50--61pp.}; qualitative analysis confirms 75--90\% of failures stem from agent behavior, suggesting that observed failures primarily reflect agent behavior under our evaluation setup. $\tau$-voice provides a reproducible testbed for measuring progress toward voice agents that are natural, conversational, and reliable.

