\section{Results}
\label{sec:results}

\subsection{Quantitative Results}

\subsubsection{Task Completion}

Figure~\ref{fig:headline} and Table~\ref{tab:text-control-regular} present our headline finding: \textbf{voice agents show substantial drops from text baselines}. Under \textbf{Clean} conditions (studio-quality audio, American accents), the best voice provider already drops 34pp from GPT-5 (51\% vs GPT-5 at 85\%).\revised{Was 38pp (42\% vs 80\%). Best Clean improved from 42\% to 51\% due to new OpenAI model; text baseline rose from 80\% to 85\% due to updated tasks.} Under \textbf{Realistic} conditions (background noise, diverse accents, natural user behaviors), performance drops an additional 13pp to 38\%---voice agents retain only 30--45\% of text SOTA capability.\revised{Was ``additional 12pp to 30\%''. Relative framing (``retains 30--45\%'') is new; lower bound rose from 29\% to 30\% due to Google improvement.} Against non-reasoning text models, the best voice provider nearly matches GPT-4.1 (54\%) under Clean conditions (51\%, just 3pp gap) but still drops 16pp under Realistic.\revised{Previously a 12pp Clean gap and 24pp Realistic gap vs GPT-4.1. The Clean gap has nearly closed (3pp).}

\begin{table}[h]
\caption{Text vs Voice comparison (pass@1). Text shows GPT-5 (reasoning) and GPT-4.1 (non-reasoning). Voice evaluated under Clean and Realistic conditions. Deltas show gap from GPT-5.}
\label{tab:text-control-regular}
\centering
\begin{small}
\resizebox{\columnwidth}{!}{%
\input{results/combined_comparison_table}
}
\end{small}
\end{table}

The Clean-to-Realistic drop varies substantially across providers: just 5pp for Google (8\% of its total voice-text gap) versus 13pp for xAI and OpenAI (roughly one-quarter of their total gap). For most providers, the dominant source of the voice-text gap is the drop from text to Clean voice, not the additional Realistic degradation.\revised{Google degradation was 4pp (7\%); now 5pp (8\%). Still highlights provider variance vs others at $\sim$25\%.}

Across providers, \textbf{xAI achieves the highest scores} (51\% Clean, 38\% Realistic)\revised{Was 42\%/30\%. All providers improved; competitive gap tightened from 11pp to 3pp in Realistic.}, while \textbf{Google shows the smallest absolute degradation} under realistic conditions ($-$5pp vs $-$13pp for others). In relative terms, Google loses 18\% of its Clean performance compared to 26--28\% for others---a 1.5$\times$ robustness advantage, though partly explained by Google's lower baseline leaving less to lose.\revised{Relative delta analysis is new. Google degradation grew from $-$4pp to $-$5pp (relative: 15\%$\to$18\%). Robustness advantage narrowed from 2$\times$ to 1.5$\times$.} Domain-specific patterns emerge: xAI substantially outperforms others in Telecom (58\% Clean vs 20--28\% for others), while in Retail OpenAI leads with 69\% Clean---the single best per-domain score in the benchmark---but also suffers the largest relative degradation ($-$37\%).\revised{OpenAI retail leadership is new (was 39\% Clean with old model). Relative degradation framing is new.}

\needsupdate{Re-run statistical reliability analysis with gpt-realtime-1.5. Numbers below are from the original submission's model set (gpt-realtime-2025-08-28).}
\paragraph{Statistical Reliability.} For Retail, where we conducted 3 independent runs per condition, both the text-to-Clean gap and the Clean-to-Realistic gap are statistically significant (non-overlapping 95\% CIs). Voice providers achieve 36--39\% $\pm$ 3--6pp (Clean) and 12--26\% $\pm$ 2--4pp (Realistic), compared to text baselines of 73\% $\pm$ 3pp (GPT-4.1) and 82\% $\pm$ 1pp (GPT-5). Full statistical breakdown in Appendix~\ref{app:stat-sig}.

\subsubsection{Impact of Acoustic Realism}

To isolate which factors hurt performance most, we conduct ablations on the Retail domain, adding noise, accents, or user behaviors independently (Table~\ref{tab:ablation-single}).

\input{results/ablation_table_single}

\textbf{Accents are the most damaging factor on average}, causing a 10pp average drop (vs 4pp for noise, 7pp for user behaviors).\revised{Was 13pp accents, 9pp noise, 5pp behavior in original. Accents now 10pp, noise 4pp, behavior 7pp---behavior more than doubled.} However, the accent effect is highly provider-specific: xAI is severely affected ($-$19pp, $-$40\% relative), while Google is nearly unaffected ($-$1pp, $-$2\% relative).\revised{Previously framed as universal ($-$13pp). Now xAI-specific ($-$19pp); Google nearly flat ($-$1pp).} This finding has accessibility implications, particularly for xAI users with non-American accents. Because accents are implemented via TTS personas, these results should be interpreted as indicative rather than definitive.

\textbf{Interactions between factors are complex and provider-specific.}\revised{Previously: ``Google is consistently most robust; individual effects sum to $-$5pp, full Realistic $-$11pp.'' Google's individual sum is now $-$16pp (was +6pp in intermediate); interaction changed from super-additive to nearly additive.} For Google, individual factors sum to $-$16pp and the full Realistic condition causes $-$14pp---a nearly additive interaction where individual effects approximately predict the combined outcome. Behavior is Google's worst single factor ($-$11pp, $-$24\% relative). For xAI, the pattern reverses: individual factors sum to $-$20pp, yet the full Realistic drop is only $-$11pp---accents alone devastate xAI ($-$19pp), but adding noise and user behaviors partially compensates. Notably, OpenAI has both the highest Clean score (69\%) and the largest relative Realistic degradation ($-$37\%), suggesting that higher baseline capability does not protect against---and may amplify---the impact of speech complexity.\revised{OpenAI vulnerability paradox and relative degradation framing are new.}

\subsubsection{Voice Interaction Quality}

Beyond task completion, we evaluate conversational dynamics under Realistic conditions (Table~\ref{tab:voice-quality}). We report four aggregate dimensions: \textbf{Latency} (how quickly agents react), \textbf{Responsiveness} (whether agents act when needed), \textbf{Interrupt} (how often agents cut off users mid-speech), and \textbf{Selectivity} (whether agents correctly ignore signals that do not require action).

\begin{table}[h]
\caption{Voice interaction quality (Realistic condition, aggregated across domains). \textbf{Bold} indicates best. Full breakdown in Appendix~\ref{app:voice-metrics-detail}.}
\label{tab:voice-quality}
\centering
\begin{small}
\resizebox{\columnwidth}{!}{%
\input{results/voice_quality_aggregated_table}
}
\end{small}
\end{table}

\revised{Voice quality section fully rewritten. All three provider characterizations changed due to new OpenAI model (gpt-realtime-1.5). Previously: xAI fastest (0.99s), OpenAI slowest (2.22s) and most selective (74\%), Google most balanced. Now: OpenAI fastest (0.90s) and least selective (6\%), xAI highest interrupt, Google most balanced with best selectivity.}

\textbf{OpenAI achieves the best latency and responsiveness}: fastest reactions (0.90s) and near-perfect responsiveness (100\%). However, this comes at a severe cost to selectivity: OpenAI's selectivity is just 6\%---it responds to nearly all backchannels, vocal tics, and non-directed speech. Despite this, OpenAI achieves top-tier task completion, suggesting that a ``respond to everything'' strategy can be surprisingly effective for task success while being poor conversational behavior.

\textbf{xAI shows strong but uneven dynamics}: high responsiveness (83\%) and moderate latency (1.15s), but the highest interrupt rate (84\%)---interrupting users nearly once per turn. xAI pairs the best task completion with the worst interruption behavior. Its selectivity (57\%) is tied with Google for best.

\textbf{Google achieves the best balance}: lowest interrupt rate (21\%), reasonable latency (1.09s), and highest selectivity (57\%), though with the lowest responsiveness (68\%).\revised{Google interrupt was 21\%, unchanged; responsiveness was 65\%, now 68\%.} No provider excels across all four conversational dimensions, highlighting the fundamental challenge of real-time turn-taking.

\subsection{Qualitative Error Analysis}
\label{sec:analysis}

To characterize failure modes beyond aggregate pass rates---and to verify that observed failures stem from agent behavior rather than artifacts of the benchmark or user simulator---we perform a qualitative error analysis.\footnote{This analysis was conducted on the original submission's model set (including \texttt{gpt-realtime-2025-08-28}). The qualitative findings on error sources and types are expected to generalize, though the specific distribution may differ with \texttt{gpt-realtime-1.5}.}

\paragraph{Task Selection.} We define $\text{pass}_{\text{text}}$ as tasks where both GPT-4.1 and GPT-5.2 (medium reasoning) succeed in text mode, $\text{pass}_{\text{clean}}$ as tasks where a majority of audio providers succeed under Clean conditions, and $\text{pass}_{\text{realistic}}$ as tasks where a majority succeed under Realistic conditions. We construct two analysis cohorts:
\begin{itemize}[nosep,leftmargin=*]
    \item \textbf{Voice-Fragile}: Tasks that satisfy $\text{pass}_{\text{text}}$ but not $\text{pass}_{\text{clean}}$, isolating inherent voice interaction challenges.
    \item \textbf{Noise-Fragile}: Tasks that satisfy $\text{pass}_{\text{clean}}$ but not $\text{pass}_{\text{realistic}}$, isolating the impact of acoustic realism (noise, accents, interruptions).
\end{itemize}
For each cohort, we sample 20 tasks, prioritizing those exhibiting the largest performance gap between conditions. For each sampled task, we randomly select one failing provider for analysis.

\paragraph{Annotation Procedure.} Two independent raters examined each failed simulation, labeling: (1) \textit{error source}---whether the agent or user simulator caused the first critical error; and (2) \textit{error type}---one of logical, transcription, VAD/unresponsive, hallucination, or early termination. Inter-rater agreement was 92.5\% (37/40 tasks); disagreements were resolved through discussion.

\paragraph{Results.} Table~\ref{tab:combined-error-analysis} shows the distribution of error types by source for both cohorts. Full annotations are in Appendix~\ref{app:qualitative-analysis}.

\begin{table}[h]
\caption{Error analysis: distribution of error types by source. Agent errors dominate in both cohorts (75\% and 90\%).}
\label{tab:combined-error-analysis}
\centering
\begin{small}
\resizebox{0.85\columnwidth}{!}{%
\input{results/combined_error_analysis}
}
\end{small}
\end{table}

\textbf{Agent errors dominate}: 75\% of failures in the Voice-Fragile cohort and 90\% in the Noise-Fragile cohort are attributed to the agent rather than the user simulator---suggesting that observed failures primarily reflect agent behavior under our evaluation setup, not simulator artifacts.

\textbf{Logical errors are most common in the Voice-Fragile cohort} (8/20), indicating that voice agents struggle with reasoning even when transcription is accurate. However, \textbf{VAD/unresponsive errors become dominant in the Noise-Fragile cohort} (8/20), where background noise and interruptions cause agents to miss user utterances or become unresponsive.
